Supplement

### 2023-10-12 paper/manuscript.Rmd
work on edits; redo tieu

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size (interquartile range `r round(ratio_dist[2]*100)`%-`r round(ratio_dist[4]*100)`%)^[Replications had a median of `r round(rep_dist[3])` participants (interquartile range: `r round(rep_dist[2])` - `r round(rep_dist[4])`), while original studies had a median of `r round(target_dist[3])` participants (interquartile range: `r round(target_dist[2])` - `r round(target_dist[4])`).].  In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).

@@

```
## Bivariate correlates of replication success

@@

Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data. Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).  While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient). These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).

@@

Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, `r nrow(ps)`, `r round( nrow(ps)/nrow(all)*100)`% of studies).

>>>>

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size.  In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).

@@

## Bivariate correlates of replication success

@@

Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data. Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).  While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient). These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications. However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends. Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).

@@

Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to `r nrow(ps)` Psych Science articles in the replication sample, `r round( nrow(ps)/nrow(all)*100)`% of all studies).

### 2023-10-12 paper/manuscript.tex
work on edits; redo tieu

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was 86\% of the original sample size (interquartile range 41\%-105\%)\footnote{Replications had a median of 59 participants (interquartile range: 31 - 124), while original studies had a median of 101 participants (interquartile range: 40 - 180).}. In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).

@@

@@

\caption{\label{tab:unnamed-chunk-6}Descriptive properties of the replication dataset. For categorical features, counts and percentages are given. For continuous features, the median value and interquartile range are given. N=176 except for original effect size and p-value where N=112. }
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lc}
\toprule
Feature & Summary\\
\midrule
Subfield & \\
\hspace{1em}Cognitive & 62 (35\%)\\
\hspace{1em}Social & 70 (40\%)\\
\hspace{1em}Other psych & 24 (14\%)\\
\hspace{1em}Non-psych & 20 (11\%)\\
Open data & 52 (30\%)\\
Open materials & 83 (47\%)\\
Switch from in-person to online & 94 (53\%)\\
Original authors at Stanford & 16 (9.1\%)\\
Within subjects design & 80 (45\%)\\
Single vignette & 78 (44\%)\\
Number of trials & 6 (1, 60)\\
Publication Year & 2015 (2011, 2017)\\
Original sample size & 101 (40, 181)\\
Replication sample size & 59 (31, 125)\\
Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
Original effect size (SMD) & 0.61 (0.46, 0.98)\\
Original p-value & 0.0001 (0.0000, 0.0069)\\
\bottomrule
\end{tabular}
\end{table}

@@

Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data. Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{31}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient). These factors -- open materials, open data, and online samples -- are more common in more recent studies, and so these effects may partially reflect temporal trends (see Figure \ref{fig:corr-plot} for the correlations between these factors and publication year).

@@

Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample, 80, 45\% of studies).

>>>>

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was 86\% of the original sample size. In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).

@@

\caption{\label{tab:unnamed-chunk-4}Descriptive properties of the replication dataset. For categorical features, counts and percentages are given. For continuous features, the median value and interquartile range are given. N=176 except for original effect size and p-value where N=112. }
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lc}
\toprule
Feature & Summary\\
\midrule
Subfield & \\
\hspace{1em}Cognitive & 62 (35\%)\\
\hspace{1em}Social & 70 (40\%)\\
\hspace{1em}Other psych & 24 (14\%)\\
\hspace{1em}Non-psych & 20 (11\%)\\
Open data & 52 (30\%)\\
Open materials & 83 (47\%)\\
Switch from in-person to online & 94 (53\%)\\
Original authors at Stanford & 16 (9.1\%)\\
Within subjects design & 80 (45\%)\\
Single vignette & 78 (44\%)\\
Number of trials & 6 (1, 60)\\
Publication Year & 2015 (2011, 2017)\\
Original sample size & 101 (40, 181)\\
Replication sample size & 59 (31, 125)\\
Ratio of replication/original sample sizes & 0.86 (0.41, 1.05)\\
Original effect size (SMD) & 0.61 (0.46, 0.98)\\
Original p-value & 0.0001 (0.0000, 0.0069)\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

Studies with open data, which almost always also had open materials as well, tended to replicate more than studies without open data. Nearly all replication studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{31}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (e.g., inductions might have been weaker or instructions might have been insufficient). These factors -- open materials, open data, and online samples -- may have all contributed to the closeness of the replications. However, they are also practices that have increased over time, and so these effects may partially reflect temporal trends. Nonetheless, publication year only very weakly correlated with replicability, but does correlate strongly with online samples and openness (Figure \ref{fig:corr-plot}).

@@

Students were free to choose what study to replicate; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to 80 Psych Science articles in the replication sample, 45\% of all studies).

### 2023-10-12 paper/supplement.Rmd
work on edits; redo tieu

>>>>

# Sub sample of Psych Science papers

```{r}
all <- read_csv(here("data", "raw_data.csv")) |> filter(include %in% c("stats", "pred_int", "exp"))

ps <- all|> mutate(journal=str_to_lower(journal)) |>filter(journal=="psych sci")

We were unable to use journal as a predictor in the models because of very uneven representation across journals. By far the most represented journal was Psychological Science, with `r nrow(ps)` original papers. Other journals had at most a few papers in the sample.

Here we present bivariate analyses on the subset of the data coming from Psych Science. This is a post-hoc split of the data.

Overall, this split looks similar to the overall sample. Of note, publication year is correlated with replication success in this sample, but is not substantially correlated overall.

```{r}
library(gtsummary)
theme_gtsummary_language("en", big.mark = "")
library(kableExtra)

all_label <- all %>% select(target_lastauthor_year,journal)

desc <- d %>% left_join(all_label) %>% 
  mutate(journal=str_to_lower(journal)) |>
  filter(journal=="psych sci") %>% 
  mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
         ss_ratio=replication_N/target_N)%>% 
  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>% 
  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
         within_between=ifelse(within_between=="between", 0, 1)) %>% 
             tbl_summary(
               label=list(
                 subfield ~ "Subfield",
                 stanford_internal ~ "Original authors at Stanford",
                 target_year~ "Publication Year",
                 single_vignette ~ "Single vignette",
                 open_data ~ "Open data",
                 open_materials ~ "Open materials",
                 within_between ~ "Within subjects design",
                 repeated_measure ~ "Number of trials",
                 target_N ~ "Original sample size",
                 replication_N ~ "Replication sample size",
                 ss_ratio ~ "Ratio of replication/original sample sizes",
                 target_d_calc ~"Original effect size (SMD)",
                 target_p_calc ~ "Original p-value",
                 switch_modality ~ "Switch from in-person to online"
               ),
               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
               digits=list(target_year ~ 0, target_p_calc ~4),
    missing="no",
             ) %>% 
modify_header(label="Feature", stat_0="Summary") %>% 
    modify_footnote(update = everything() ~ NA)

as_kable_extra(desc,format="latex", position="!h", caption="Descriptive properties of the Psych Science portion of the replication dataset. For categorical features, counts and percentages are given. For continuous features, the median value and interquartile range are given. ", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)

```{r cor}

for_cor <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |>
  left_join(all_label) %>% 
  mutate(journal=str_to_lower(journal)) |>
  filter(journal=="psych sci") %>% 
  select(sub_rep, 
         pub_year, subfield, open_data, open_mat, stanford, change_platform, log_ratio_ss, is_within, single_vignette, log_sample, log_trials) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0))

sub_cor <- function(var, stat = "estimate") {
  if (stat == "estimate") {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
  } else {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
  }
}

preds <- c("pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
           "log_trials", "social", "other_psych", "non_psych")

cors <- tibble(preds = preds) |>
  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psychology (versus cognitive psych)", "Other psychology (versus cognitive psych)", "Non psychology (versus cognitive psych)", "Within participants design (versus between participants)", "Single vignette (versus multiple items/inductions per condition)", "Switch to online for replication (versus same modality for original and replication)", "Open data", "Open materials", "Stanford affiliation of original authors at time of replication", "Publication year", "Log number of  trials", "Log original sample size", "Log ratio between replication and original sample sizes"))) |> arrange(desc(r)) |> select(r, p, Predictors)

library(kableExtra)
knitr::kable(cors, digits = 3, align='ccl',format="latex", position="!h", caption="The unadjusted Pearson correlations between each individual predictor and the subjective replication score for the Psych Science subsample.", booktabs=TRUE, linesep="") |> kable_styling(full_width=F, font_size=10)
